---
title: "scrapbook"
author: "Ben Smith"
date: "7/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The data dictionary is availbale here: https://docs.google.com/spreadsheets/d/1ecjSi3d3bOnaAsudMnP80-MkI4GSrRoT6_I6r3xUM3Q/edit#gid=0



For most behaviours, codes are:
  
  
SCRUB data dictionary
100%

1, Never | 2, Rarely | 3, Sometimes | 4, Often | 5, Always | 99, N/A
To enable screen reader support, press ⌘+Option+Z To learn about keyboard shortcuts, press ⌘slash
 

The following behaviours have a different set of choices:
 
 - OTHB_TREAT_CONV
 - OTHB_CANCEL_TRAVEL
 - OTHB_SAVE_MONEY
 - OTHB_CANCEL_SMALL
 - OTHB_CANCEL_LARGE
 - OTHB_CANCEL_VULN
 - OTHB_WEAR_MASK
 
 
Their choices are marked
 		


1, Not at all | 2, A little | 3, A moderate amount | 4, A lot | 5, A great deal | 99, N/A

```{r}
library(data.table)
data_file <- "latest_open_science_data.RDS"
dat <- readr::read_rds(data_file)
  
dat$gender <- sjlabelled::replace_labels(dat$gender, labels = c("Male" = 1, "Female" = 2, "Other" = 3))
col_values <- get_values(dat$beh_handwash)
col_labels <- get_labels(dat$beh_handwash)
dat$beh_handwash <- factor(dat$beh_handwash,levels=col_values,labels=col_labels,ordered = TRUE)

names(dat)[-1:-5]

```

