---
title: "scrapbook"
author: "Ben Smith"
date: "7/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The data dictionary is availbale here: https://docs.google.com/spreadsheets/d/1ecjSi3d3bOnaAsudMnP80-MkI4GSrRoT6_I6r3xUM3Q/edit#gid=0



For most behaviours, codes are:
  
  
SCRUB data dictionary
100%

1, Never | 2, Rarely | 3, Sometimes | 4, Often | 5, Always | 99, N/A
To enable screen reader support, press ⌘+Option+Z To learn about keyboard shortcuts, press ⌘slash
 

The following behaviours have a different set of choices:
 
 - OTHB_TREAT_CONV
 - OTHB_CANCEL_TRAVEL
 - OTHB_SAVE_MONEY
 - OTHB_CANCEL_SMALL
 - OTHB_CANCEL_LARGE
 - OTHB_CANCEL_VULN
 - OTHB_WEAR_MASK
 
 
Their choices are marked
 		


1, Not at all | 2, A little | 3, A moderate amount | 4, A lot | 5, A great deal | 99, N/A

```{r}
library(data.table)
data_file <- "latest_open_science_data.RDS"
dat <- readr::read_rds(data_file)
  
dat$gender <- sjlabelled::replace_labels(dat$gender, labels = c("Male" = 1, "Female" = 2, "Other" = 3))
col_values <- get_values(dat$beh_handwash)
col_labels <- get_labels(dat$beh_handwash)
dat$beh_handwash <- factor(dat$beh_handwash,levels=col_values,labels=col_labels,ordered = TRUE)

names(dat)[-1:-5]

```


```{r}
filter_stem="beh_"
plot_data <- dplyr::select(dat, wave, agegroup, gender, state_aus, country,
                                    starts_with(filter_stem), -contains("other"),
                                    -contains("_pa_"), -contains("alcohol"), -contains("w3"))

plot_data$wave <- dplyr::recode(factor(plot_data$wave),
                                '1' = "March",
                                '2' = "April",
                                '3' = "May",
                                '4' = "June")
for(var in colnames(plot_data)[-1:-5]) {
  names(plot_data)[which(var==colnames(plot_data))] <- attr(plot_data[,deparse(as.name(var))], "label")
}


groupByStackedBar <- function(df, field) {
  #we will need to summarise the percentages separately for each group, I think.
  #or we just reshape, right
  #start something like this:
  df %>% 
    group_by_(field) %>% filter(n() >= 20) %>% ungroup() %>% 
    #then gather the question data all into one column
    tidyr::gather(key="Question",value="value",6:ncol(.)) %>%
    filter(!is.na(value)) %>%
    #group it by both question and the field
    group_by_(field,"Question") %>% 
    #tally
    count(value) %>%
    mutate(percentage=n/sum(n))
}
by <- "agegroup"

m <- groupByStackedBar(plot_data, by)


    m <- groupByStackedBar(plot_data, by)
    m <- mutate(m, q2=Question)
    only_one_wave <- table(m$Question)==1*length(unique(m$value))
    multiple_waves <- names(only_one_wave)[!only_one_wave]
    m <- filter(m, Question %in% multiple_waves)
    names(m)[1] <- "group"
    m <- dplyr::filter(m, !is.na(group))
    m$group <- dplyr::recode(m$group,
                             'Australian Capital Territory' = "ACT",
                             'United Kingdom of Great Britain and Northern Ireland' = "UK",
                             'United States of America' = "USA")
    

```

```{r}
#print(names(plot_data)[length(plot_data)])
y_values <- attr(plot_data[,names(plot_data)[length(plot_data)]],"labels")
y_labels <- names(y_values)
    
    m$value<-factor(m$value,levels = rev(y_values),labels=rev(y_labels))
    m$group<-factor(m$group,ordered=TRUE)
```


```{r}
m_subset<-m %>% filter(Question==m$Question[[1]])
m_subset$group<-as.numeric(m_subset$group)
```

```{r}
m <- m %>% arrange(value)
```


```{r}
library(plotly)
m_plot<-
    m %>%
      ggplot( aes(x=group, y=percentage,fill=value)) +
      geom_bar(size=1,alpha=0.8,stat="identity",position="stack")+
      # geom_line( data=m %>% dplyr::select(-Question), aes(group=q2), color="grey", size=0.5, alpha=0.5) +
      # geom_line( aes(group=Question), color="#69b3a2", size=1.2 )+
      # geom_ribbon(aes(group=Question), color=NA, fill="#69b3a2", alpha=0.1)+
      scale_y_continuous(labels=scales::percent_format())+
      scale_fill_brewer(palette="RdYlBu",direction=-1)+
      #ggthemes::theme_fivethirtyeight() +
      theme(
        legend.position="bottom",
        panel.grid = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 1),
        plot.margin = margin(t = 10, r = 10, b = 5, l = 10, unit = "pt"),
        axis.text.y = element_text(size=10,face="bold"),
        axis.text.x = element_text(size=10,face="bold", angle = 45, hjust = 1),
        strip.text.x = element_text(size=10,face="bold"),
        strip.background.x = element_rect(size=50,colour="black")
      ) +
      facet_wrap(~Question, dir = "v",
                 ncol = 3,
                 labeller = labeller(Question = label_wrap_gen(30))) 

ggplotly(m_plot)
```


